Borel regularity for ODEs and exponential integrals

### 2023-03-12 exp-resurgence.tex
Fix equation references

In this example, $v_1$ and $v_{-1}$ happen to be related by a symmetry: the M\"{o}bius transformation that pulls $\zeta$ back to $-\zeta$. Kummer's solutions typically come from six different hypergeometric equations, which are related by the M\"{o}bius transformations that permute their singularities. In our case, though, exchanging $1$ with $-1$ keeps equation~\eqref{diff-eq:spatial-mod-bessel-AL} the same.
\subsubsection{Abstract argument for Borel regularity}\label{bessel-regularity-AL}
The analysis in Sections~\ref{big-idea}--\ref{neg-root-AL} picks out a frame in the space of analytic solutions of~\eqref{diff-eq:reg-mod-bessel-AL}. The frame is generated by solutions of the form $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$, with $v_\alpha \in \zeta_\alpha^{-1/2} + o\big(\zeta_\alpha^{-1/2}\big)$.
\color{DarkTurquoise}
\begin{quote}
We get $v_\alpha$ from the existence result in Section~\ref{frac_int_exist}, which gives $v_\alpha = \zeta^{\tau-1} + v_\alpha'$ with $\tau \in (0, \infty)$ and $v_\alpha' \in \holoL{\infty, 1-\tau-\epsilon}(\Omega)$ for some $\epsilon \in (0, 1]$. Looking back at the definitions of our weighted $L^\infty$ spaces, we can see that
\begin{align*}
v_\alpha' \in \holoL{\infty, 1-\tau-\epsilon}(\Omega) & \Longrightarrow \zeta_\alpha^{1-\tau-\epsilon}\,v_\alpha' \text{ is bounded near } \zeta_\alpha = 0 \\
& \Longrightarrow \zeta_\alpha^\epsilon\,\zeta_\alpha^{1-\tau-\epsilon}\,v_\alpha' \text{ goes to } 0 \text{ as } \zeta_\alpha \text{ goes to } 0 \\
& \Longrightarrow \zeta_\alpha^{1-\tau}\,v_\alpha' \text{ goes to } 0 \text{ as } \zeta_\alpha \text{ goes to } 0 \\
& \Longrightarrow v_\alpha' / \zeta_\alpha^{\tau-1} \text{ goes to } 0 \text{ as } \zeta_\alpha \text{ goes to } 0 \\
& \Longleftrightarrow v_\alpha' \in o\big(\zeta_\alpha^{\tau-1}\big).
\end{align*}
In this case, $\tau = \tfrac{1}{2}$.
\end{quote}
\color{black}

The Poincar\'{e} algorithm, as we saw in Section~\textbf{[asymptotic analysis]}, picks out a frame in the space of formal trans-series solutions of equation~\eqref{diff-eq:reg-mod-bessel-AL}. The frame is generated by trans-monomial solutions of the form $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$, with $\tilde{W}_\alpha \in \C\llbracket z^{-1} \rrbracket$. We'll now show that if these solutions are Borel-summable, their Borel sums generate the same frame as $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$.

>>>>

In this example, $v_1$ and $v_{-1}$ happen to be related by a symmetry: the M\"{o}bius transformation that pulls $\zeta$ back to $-\zeta$. Kummer's solutions typically come from six different hypergeometric equations, which are related by the M\"{o}bius transformations that permute their singularities. In our case, though, exchanging $1$ with $-1$ keeps equation~\eqref{diff-eq:spatial-mod-bessel-AL} the same.
\subsubsection{Abstract argument for Borel regularity}\label{bessel-regularity-AL}
The analysis in Sections~\ref{big-idea}--\ref{neg-root-AL} picks out a frame in the space of analytic solutions of~\eqref{eqn:reg-mod-bessel-AL}. The frame is generated by solutions of the form $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$, with $v_\alpha \in \zeta_\alpha^{-1/2} + o\big(\zeta_\alpha^{-1/2}\big)$.
\color{DarkTurquoise}
\begin{quote}
We get $v_\alpha$ from the existence result in Section~\ref{frac_int_exist}, which gives $v_\alpha = \zeta^{\tau-1} + v_\alpha'$ with $\tau \in (0, \infty)$ and $v_\alpha' \in \holoL{\infty, 1-\tau-\epsilon}(\Omega)$ for some $\epsilon \in (0, 1]$. Looking back at the definitions of our weighted $L^\infty$ spaces, we can see that
\begin{align*}
v_\alpha' \in \holoL{\infty, 1-\tau-\epsilon}(\Omega) & \Longrightarrow \zeta_\alpha^{1-\tau-\epsilon}\,v_\alpha' \text{ is bounded near } \zeta_\alpha = 0 \\
& \Longrightarrow \zeta_\alpha^\epsilon\,\zeta_\alpha^{1-\tau-\epsilon}\,v_\alpha' \text{ goes to } 0 \text{ as } \zeta_\alpha \text{ goes to } 0 \\
& \Longrightarrow \zeta_\alpha^{1-\tau}\,v_\alpha' \text{ goes to } 0 \text{ as } \zeta_\alpha \text{ goes to } 0 \\
& \Longrightarrow v_\alpha' / \zeta_\alpha^{\tau-1} \text{ goes to } 0 \text{ as } \zeta_\alpha \text{ goes to } 0 \\
& \Longleftrightarrow v_\alpha' \in o\big(\zeta_\alpha^{\tau-1}\big).
\end{align*}
In this case, $\tau = \tfrac{1}{2}$.
\end{quote}
\color{black}

The Poincar\'{e} algorithm, as we saw in Section~\textbf{[asymptotic analysis]}, picks out a frame in the space of formal trans-series solutions of equation~\eqref{eqn:reg-mod-bessel-AL}. The frame is generated by trans-monomial solutions of the form $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$, with $\tilde{W}_\alpha \in \C\llbracket z^{-1} \rrbracket$. We'll now show that if these solutions are Borel-summable, their Borel sums generate the same frame as $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$.
